### 2023-09-03 sections/2-methods.tex
kill smallcaps

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{images/geometry/geometry.pdf}
    \caption{Scaling behavior of radii in the worst case two-dimensional scenario, 
    a uniform-density disk. $R_0$ denotes the radius of the root cluster $C_0$, and $o_0$ denotes its center. 
    After one application of Algorithm~\ref{1}, we have $C_1$, with radius $R_1$ and center $o_1$.
    The right triangle formed by $o_0$, $o_1$, and $y_+$ in $C_1$ shows that $R_0 \leq R_1$.
    Hence, the radius of a child cluster can be larger than its parent. However, 
    after another application of Algorithm~\ref{1}, we have consumed all $d$ orthogonal axes, 
    as shown in $C_2$. Now, clearly $R_2 \leq R_0$. In fact, for each subsequent application of Algorithm~\ref{1},
    the radius of the resulting cluster is bounded above by $\frac{\sqrt{2}R}{2}$.}
    \label{fig:methods:scaling_behavior}
\end{figure}

@@

To determine the asymptotic complexity of fine search, we must estimate $|F|$, the 
number of clusters for which we must look at all of the cluster's points. With $\rho$-NN 
search, $F$ is the union of clusters which are within a distance of $r + \hat{r_c}$ from the query,
where $r$ is the search radius and $\hat{r_c}$ is the mean radius of leaf clusters,
as in \cite{yu2015entropy}. With $k$-NN by Repeated $\rho$-NN, however, 
the value of $r$ is dependent on the distance to the $k$th nearest neighbor, which 
is query-dependent. Thus, for $k$-NN by Repeated $\rho$-NN, we adjust the definition of 
$F$ to be the union of clusters which are within a distance of $r' + \hat{r_c}$ from the query, 
where $r'$ is the distance to the $k$th nearest neighbor and $\hat{r_c}$ is defined as before.

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{images/geometry/geometry.pdf}
    \caption{Scaling behavior of radii on a uniform-density disk, which in two dimensions represents the worst-case scenario. 
    $R_0$ denotes the radius of the root cluster $C_0$, and $o_0$ denotes its center. 
    After one application of Algorithm~\ref{1}, we have $C_1$, with radius $R_1$ and center $o_1$.
    The right triangle formed by $o_0$, $o_1$, and $y_+$ in $C_1$ shows that $R_0 \leq R_1$.
    Hence, the radius of a child cluster can be larger than its parent. However, 
    after another application of Algorithm~\ref{1}, we have consumed all $d$ orthogonal axes, 
    as shown in $C_2$. 
    Now, clearly $R_2 \leq R_0$. In fact, for each subsequent application of Algorithm~\ref{1},
    the radius of the resulting cluster is bounded above by $\frac{\sqrt{2}R}{2}$.}
    \label{fig:methods:scaling_behavior}
\end{figure}

@@

To determine the asymptotic complexity of fine search, we must estimate $|F|$, the 
number of clusters for which we must look at all of the cluster's points. With $\rho$-NN 
search, $F$ is the union of clusters which are within a distance of $r + \hat{r_c}$ from the query,
where $r$ is the search radius, and $\hat{r_c}$ is the mean radius of leaf clusters,
as in \cite{yu2015entropy}. With $k$-NN by Repeated $\rho$-NN, however, 
the value of $r$ is dependent on the distance to the $k$th nearest neighbor, which 
is query-dependent. Thus, for $k$-NN by Repeated $\rho$-NN, we adjust the definition of 
$F$ to be the union of clusters which are within a distance of $r' + \hat{r_c}$ from the query, 
where $r'$ is the distance to the $k$th nearest neighbor and $\hat{r_c}$ is defined as before.
